oREV item selection

### 2022-11-07 analysis/irt_analysis.Rmd
prep DIF Rasch

```{r}
irt1_dif_sex <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "logit"),
  correct ~ 1 + (0+ sex | targetWord) + (1 | subjID),
  prior = prior_1pl,
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  cores = 6,
  chains = 6,
  iter = 6000
)%>%add_criterion(c("loo","waic"))

saveRDS(irt1_dif_sex, "../saves/irt1_dif_sex.rds")

irt1_dif_sex <- readRDS("../saves/irt1_dif_sex.rds")

@@

>>>>

@@

```{r}
irt1_dif_sex_sel <- brm(
  data = irt_dat_sel,
  family = brmsfamily("bernoulli", "logit"),
  correct ~ 1 + (0+ sex | targetWord) + (1 | subjID),
  prior = prior_1pl,
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  cores = 6,
  chains = 6,
  iter = 6000
)%>%add_criterion(c("loo","waic"))

saveRDS(irt1_dif_sex_sel, "../saves/irt1_dif_sex_sel.rds")

irt1_dif_sex_sel<- readRDS("../saves/irt1_dif_sex_sel.rds")

#### Order

```{r}
irt1_dif_order_sel <- brm(
  data = irt_dat_sel,
  family = brmsfamily("bernoulli", "logit"),
  correct ~ 1 + (0+ order | targetWord) + (1 | subjID),
  prior = prior_1pl,
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  cores = 6,
  chains = 6,
  iter = 6000
)%>%add_criterion(c("loo","waic"))

saveRDS(irt1_dif_order_sel, "../saves/irt1_dif_order_sel.rds")

irt1_dif_order_sel<- readRDS("../saves/irt1_dif_order_sel.rds")

```{r}
mc_dif_rasch <- loo_compare(irt1_sel, irt1_dif_sex_sel, irt1_dif_order_sel)%>%as_tibble(rownames = "model")

write_csv(mc_dif_rasch, "../saves/model_comparison_dif_rasch_sex.csv")
```

### 2022-11-07 analysis/item_selection.Rmd
prep DIF Rasch

item_sel_rasch%>%
  group_by(targetWord)%>%
  summarise(n = n()/max(iter))%>%
  ggplot(aes(x = reorder(targetWord, -n), y = n))+
  geom_bar(stat = "identity", col = "black", fill = "white")+
  labs(x = "Item", y = "Proportion selected")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

>>>>

item_sel_rasch%>%
  group_by(targetWord)%>%
  summarise(n = n()/max(iter))%>%
  ggplot(aes(x = reorder(targetWord, -n), y = n))+
  geom_bar(stat = "identity", col = "black", fill = "white")+
  labs(x = "Item", y = "Proportion selected")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

frq_sel_items_rasch <- item_sel_rasch%>%
  group_by(targetWord)%>%
  summarise(n = n()/max(iter))%>%
  arrange(-n)%>%
  slice(1:20)%>%
  pull(targetWord)

saveRDS(frq_sel_items_rasch, "../saves/selected_items_rasch.rds")
```
